%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Modified by:
% Sean McKenna for my custom header
%
% Original author:
% Rensselaer Polytechnic Institute 
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{friggeri-cl}

% MARGINS (move top of document, align date to the left)
% \topmargin=0.5in
\let\raggedleft\raggedright

\begin{document}



% TO ADDRESS
\begin{letter}{Mrs. Jane Smith \\
Recruitment Officer \\
The Corporation \\
123 Pleasant Lane \\
City, State 12345} 



% CUSTOM HEADER
\header
  {$name$}
  {$jobTitle$}
  {\# $cell$}
  {\href{mailto:$email$}{$email$}}
  {\href{$website$}{$website$}}
  {\href{$linkedin$}{$linkedin$}}



% SIGNATURE
\signature{John Smith}



% OPENING
\opening{Dear Mrs. Smith,}



% LETTER CONTENT
PARAGRAPH ONE: State the reason for the letter, name the position or type of
work you are applying for and identify the source from which you learned of the
opening (i.e. career development center, newspaper, employment service, personal
contact).

PARAGRAPH TWO: Indicate why you are interested in the position, the company, its
products, services - above all, stress what you can do for the employer. If you
are a recent graduate, explain how your academic background makes you a
qualified candidate for the position. If you have practical work experience,
point out specific achievements or unique qualifications. Try not to repeat the
same information the reader will find in the resume. Refer the reader to the
enclosed resume or application which summarizes your qualifications, training,
and experiences. The purpose of this section is to strengthen your resume by
providing details which bring your experiences to life.
 
PARAGRAPH THREE: Request a personal interview and indicate your flexibility as
to the time and place. Repeat your phone number in the letter and offer
assistance to help in a speedy response. For example, state that you will be in
the city where the company is located on a certain date and would like to set up
an interview. Alternatively, state that you will call on a certain date to set
up an interview. End the letter by thanking the employer for taking time to
consider your credentials.



% CLOSING
\closing{Sincerely yours,}



% ENCLOSED
% \encl{Curriculum vitae, employment form}



\end{letter}
\end{document}